---
title: "Decision Tree Example"
author: "Scott Stoltzman"
date: "7/17/2019"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')
library('caret')
library('GGally')
library('rpart.plot')
set.seed(123)
```

## Data
```{r}
raw_dat = as.data.frame(diamonds)
head(raw_dat)
```


## Group your prices into "high, medium, low" where price:
high = >75%
medium = 25% - 75%
low = <25%
(hint: find quartiles group data for prices)
*Replace* your price column with this new data
```{r}
price_buckets = quantile(raw_dat$price)

dat = raw_dat %>%
  mutate(price = if_else(price < price_buckets[2],
                          "low",
                          if_else(price > price_buckets[4],
                                  "high",
                                  "medium")))
```


## Randomly sample 1% of your data to visualize and plot using ggpairs
```{r, message=FALSE, warning=FALSE}
dat %>% 
  sample_n(0.01 * nrow(dat)) %>%
  GGally::ggpairs()
```


## Split data to test / train
Use 75% of the data for training 
```{r}
training_split = 0.75
smp_size = floor(training_split * nrow(dat))
dat_index = sample(seq_len(nrow(dat)), size = smp_size)
dat_train = dat[dat_index,]
dat_test = dat[-dat_index,]
```


## Create a decision tree using `caret::train` and the algorithm `rpart`
```{r}
tctrl = trainControl(method = 'cv',
                     number = 10,
                     savePredictions = TRUE,
                     classProbs = TRUE)

mod_dt = train(dat_train %>% select(-price), 
                dat_train$price, 
                method = 'rpart',
                parms = list(split = "information"),
                trControl=tctrl)

pred_dt = predict(mod_dt, dat_test, type = 'prob')
```

## Visualize your tree
Use the `prp` function
```{r}
prp(mod_dt$finalModel, box.palette = "auto")
```


## Predict whether the following diamond would be "high, medium, or low" price
```{r}
new_diamond = data.frame(
  carat = 0.92,
  cut = ordered('Premium'),
  color = ordered('J'),
  clarity = ordered('SI2'),
  depth = 63.1,
  table = 58,
  x = 4.31,
  y = 4.41,
  z = 2.70
)
predict(mod_dt, new_diamond)
```


## Create a small write up on your model

Describe your results.
Show the model parameters, confusion matrix, etc.
Explain why you chose to use the parameters you did for this decision tree model.

